fl0w 2.0 - a development environment for the\\ KIPR Wallaby

### 2017-02-09 paper.tex
Added introduction, implementation as well as components section
Components sections is still work in progress

\begin{abstract}
This publication introduces fl0w, an alternative\\ development environment for the KIPR Wallaby.\\ The aim of fl0w is to improve the robotics development\\ experience. It focuses on the components that make up fl0w, namely a file synchronization protocol that maintains a consistent state across all connected controllers, a route based and data type preserving network protocol with peer-to-peer piping capabilities, a discovery protocol that connects all controllers together automatically, a Sublime Text \cite{Sublime Text 3:Sublime HQ} plugin which enables in-line sensor readouts, program execution, program editing, and keyboard shortcuts, and a browser-based management front-end to manage the fl0w fleet.\\
\end{abstract}

\begin{IEEEkeywords}
file synchronization, networking, LAN discovery
\end{IEEEkeywords}

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

@@

@@

>>>>

\begin{abstract}
This publication introduces fl0w, an alternative\\ development environment for the KIPR Wallaby.\\ The aim of fl0w is to improve the robotics program development experience. It focuses on the components that make up fl0w, namely a file synchronization protocol that maintains a consistent state across all connected controllers, a route based and data type preserving network protocol with peer-to-peer piping capabilities, a discovery protocol that connects all controllers together automatically, a Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin which enables in-line sensor readouts, program execution, program editing, and keyboard shortcuts, and a browser-based management front-end to manage the controller fleet.\\
\end{abstract}

\begin{IEEEkeywords}
file synchronization, networking, LAN discovery, development environment
\end{IEEEkeywords}

\section{Introduction}
fl0w was developed out of a need for a fast, reliable and wireless workflow solution that can compete with the currently available offerings like Harrogate\cite{Harrogate:KIPR}. Its goals are to transform the connected controllers to a redundant fleet of logical units that share the same binaries and source code, real-time in-line sensor readouts, and a management layer inside the text editor as well as a browser-based interface.

\section{Implementation}
All fl0w components emphasize shared code and are therefor written in Python 3.3.6\cite{Python 3.3.6:Python Foundation} to remain compatible with the Sublime Text 3\cite{Sublime Text 3:Sublime HQ} plugin environment. Python was chosen as the implementation language for fl0w because of its rich standard library and its lightweight virtual machine that can run on a Wallaby controller with acceptable speed. A pre-compiled version of Python 3.3.6 \cite{Python 3.3.6:Python Foundation} is bundled with the fl0w installer because it is not present on the Wallaby by default. All fl0w components are designed as libraries to allow for integration into other projects.

\section{Components}
\subsection{undergr0und}
undergr0und\cite{undergr0und:Philip Trauner} is an asynchronous route based and data type preserving network protocol with peer-to-peer piping capabilities. The Python\cite{Python 3.3.6:Python Foundation} version is built on top of a fork of ws4py\cite{ws4py:Philip Trauner} and the JavaScript version utilizes regular WebSockets\cite{The WebSocket Protocol:A. Melnikov}. It was created to mitigate the problems fl0ws explorative development style created. Instead of one monolithic network protocol, undergr0und consists of many small sub protocols. This was done because all monolithic design would at some point become too inconsistent. undergr0und\cite{undergr0und:Philip Trauner} manages itself through its own capabilities.

\subsubsection{Pipes}
Pipes are client peer-to-peer messages piped through the server.

@@

\section*{Acknowledgment}

@@

\bibitem{Harrogate:KIPR}
KIPR, \emph{Harrogate}, \url{https://github.com/kipr/harrogate},\\ source code,
accessed February 9th 2017

\bibitem{Python 3.3.6:Python Foundation}
Python Foundation, \emph{Python 3.3.6}, \url{https://www.python.org/downloads/release/python-336/}, source code, accessed February 9th 2017

\bibitem{undergr0und:Philip Trauner}
Philip Trauner, \emph{undergr0und}, \url{https://github.com/robot0nfire/fl0w/wiki/undergr0und}, implementation notes, accessed February 9th 2017

\bibitem{ws4py:Philip Trauner}
Philip Trauner, \emph{ws4py}, \url{https://github.com/robot0nfire/ws4py}, source code, accessed February 9th 2017

\bibitem{The WebSocket Protocol:A. Melnikov}
A. Melnikov, \emph{The WebSocket Protocol}, \url{https://tools.ietf.org/html/rfc6455}, implementation notes, accessed February 9th 2017
